### 2018-06-06 2_wmm.tex
Consider final Professor's comments.

Synchronisation instructions (fences) cause \textit{barrier events}, which do not perform any computation or memory value transfer, instead, they the set of program behaviours by adding barrier relations to the program model.
Functionally, a fence may be a synchronisation barrier or a instruction for flushing memory caches into the main memory, etc.
For instance, the \texttt{mfence} instruction of the x86 assembly flushes the store buffers of the thread, and thus does not allow the \rf-relation (see Section~\ref{ch:wmm:model:relations}) to point to

>>>>

Synchronisation instructions (fences) cause \textit{barrier events}, which do not perform any computation or memory value transfer, instead, they the set of program behaviours by adding barrier relations to the program model.
Functionally, a fence may be a synchronisation barrier or a instruction for flushing memory caches into the main memory, etc.
For instance, the \texttt{mfence} instruction of the x86 assembly flushes the store buffers of the thread, and thus does not allow the \rf-relation to hold (see Section~\ref{ch:wmm:model:relations}).

### 2018-06-06 4_impl.tex
Consider final Professor's comments.

\vspace{0.5em}
\begin{enumerate}[nolistsep]
  \item \textit{Robustness:}
    \begin{enumerate}[label*=\arabic*.]
      \item completeness of the analysis,
      \item modular architecture: each module can be tested independently,
      \item usage of software design patterns where necessary, and
      \item usage of immutable data structures for all DTOs.
    \end{enumerate}
  \item \textit{Transparency:}
    \begin{enumerate}[label*=\arabic*.]
      \item following the principles of simplicity and readability,
      \item clear and informative program output, and
      \item following the clear code style.
    \end{enumerate}
  \item \textit{Efficiency:}
    \begin{enumerate}[label*=\arabic*.]%[leftmargin=1.5em]
      \item keeping the trade-off between execution time and memory usage.
    \end{enumerate}
  \item \textit{Extensibility:}
    \begin{enumerate}[label*=\arabic*.]%[leftmargin=1em]
      \item clear modular architecture.
    \end{enumerate}
\end{enumerate}

@@

The interface methods exposed by the \texttt{XMemoryManager} are presented in Figure~\ref{fig:mem-manager}.
At each time of the compilation process, the \texttt{XMemoryManager} can resolve the memory unit by its name.
Following the C standard, local memory units have higher priority over global ones (the method \lstinline{getDeclaredUnitOrNull} returns the first memory unit found, either a global one or a local one, or null if no memory units with requested name have been registered).
Since C language allows usage of variables that have the same name to be declared in nested contexts, the \texttt{XMemoryManager} should carry the stack of block contexts for local variables (which is not currently implemented).

@@

Before processing a newly emitted event, the interpreter checks whether the queue \texttt{readyContexts} is not empty.
If so, it iterates over all ready-contexts and sets up control-flow edges considering that the newly emitted event is an exit-event" of the non-linear context (e.g., for a branching context the interpreter adds primary edges from condition-event to the first-true-branch-event and from the last-true-branch-event to the exit-event, the same is done with alternative edges for the false-branch).
For the sake of simplicity of the interpretation and encoding, jump events (no-computation events) are present in the flow-graph, however they can be removed from it with rebinding ingoing and outgoing edges.
As an example of usage the interpreter, consider the code of the \texttt{Y2XConverterVisitor} for processing \texttt{if-then-else} statement of the \ytree{} in Appendix~\ref{apx:y2x}.

@@

The unrolling procedure is performed by the \texttt{XFlowGraphUnroller}.
For unrolling the flow-graph, we perform the \textit{Deep-First Search~(DFS)} while counting the X-events (for the unrolling bound) and keeping track of the depth stack (for detecting back edges needed for determining the type of sink node).
Back-edges are determined via the depth stack (each next event is pushed onto the stack; if the new event is present in the stack, the last processed edge is a back-edge).
Also, during the unrolling each next event increments the \textit{unrolling depth counter} -- the non-zero integer \textit{event reference-ID} stored by each X-event (only events of a non-unrolled graph can have the zero-valued reference-ID)
As an X-event is immutable, it has the method `\lstinline{XEvent asNodeRef(int refId)}' that clones it with new value of reference-ID.
The methods \lstinline{hashCode} and \texttt{equals} consider the reference-ID as the uniqueness field for all events except sink and source events (considering the usage of \texttt{HashMap} and Guava's \texttt{ImmutableMap} for storing events, proper setting of the hash-code methods is a crucial programming task).

>>>>

\vspace{0.5em}
\begin{enumerate}[nolistsep]
  \item \textit{Robustness:}
    \begin{enumerate}[label*=\arabic*.]
      \item completeness of the analysis,
      \item modular architecture: each module can be tested independently,
      \item use of software design patterns where necessary, and
      \item use of immutable data structures for all DTOs.
    \end{enumerate}
  \item \textit{Transparency:}
    \begin{enumerate}[label*=\arabic*.]
      \item following the principles of simplicity and readability,
      \item clear and informative program output, and
      \item following the clear code style.
    \end{enumerate}
  \item \textit{Efficiency:}
    \begin{enumerate}[label*=\arabic*.]%[leftmargin=1.5em]
      \item keeping the trade-off between execution time and memory usage.
    \end{enumerate}
  \item \textit{Extensibility:}
    \begin{enumerate}[label*=\arabic*.]%[leftmargin=1em]
      \item clear modular architecture.
    \end{enumerate}
\end{enumerate}

@@

The interface methods exposed by the \texttt{XMemoryManager} are presented in Figure~\ref{fig:mem-manager}.
At each time of the compilation process, the \texttt{XMemoryManager} can resolve the memory unit by its name.
Following the C standard, local memory units have higher priority over global ones (the method \lstinline{getDeclaredUnitOrNull} returns the first memory unit found, either a global one or a local one, or null if no memory units with requested name have been registered).
Since C language allows use of variables that have the same name to be declared in nested contexts, the \texttt{XMemoryManager} should carry the stack of block contexts for local variables (which is not currently implemented).

@@

Before processing a newly emitted event, the interpreter checks whether the queue \texttt{readyContexts} is not empty.
If so, it iterates over all ready-contexts and sets up control-flow edges considering that the newly emitted event is an exit-event" of the non-linear context (e.g., for a branching context the interpreter adds primary edges from condition-event to the first-true-branch-event and from the last-true-branch-event to the exit-event, the same is done with alternative edges for the false-branch).
For the sake of simplicity of the interpretation and encoding, jump events (no-computation events) are present in the flow-graph, however they can be removed from it with rebinding ingoing and outgoing edges.
As an example of usage of the interpreter, consider the code of the \texttt{Y2XConverterVisitor} for processing \texttt{if-then-else} statement of the \ytree{} in Appendix~\ref{apx:y2x}.

@@

The unrolling procedure is performed by the \texttt{XFlowGraphUnroller}.
For unrolling the flow-graph, we perform the \textit{Deep-First Search~(DFS)} while counting the X-events (for the unrolling bound) and keeping track of the depth stack (for detecting back edges needed for determining the type of sink node).
Back-edges are determined via the depth stack (each next event is pushed onto the stack; if the new event is present in the stack, the last processed edge is a back-edge).
Also, during the unrolling each next event increments the \textit{unrolling depth counter} -- the non-zero integer \textit{event reference-ID} stored by each X-event (only events of a non-unrolled graph can have the zero-valued reference-ID)
As an X-event is immutable, it has the method `\lstinline{XEvent asNodeRef(int refId)}' that clones it with new value of reference-ID.
The methods \lstinline{hashCode} and \texttt{equals} consider the reference-ID as the uniqueness field for all events except sink and source events (considering the use of \texttt{HashMap} and Guava's \texttt{ImmutableMap} for storing events, proper setting of the hash-code methods is a crucial programming task).

### 2018-06-06 90_summary.tex
Consider final Professor's comments.

\item 
As the tests show, the \textit{performance overhead} of the new architecture is negligible (see Section~\ref{ch:eval:perf}), therefore we consider the applied architectural changes as acceptable.

>>>>

\item 
As the tests show, the \textit{performance overhead} of the new architecture is negligible (see Section~\ref{ch:eval:perf}), therefore we consider the applied architectural decisions to be acceptable.
